### 2016-07-16 errana.tex
describing N and fixing a bug

&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2\, \big(6 ||J^*-\Phi r^*||_{\mn}

@@

+2||\Gamma J^*-\hg J^*||_{\mn}\big).

@@

The result now follows by substituting the bound on $||J^*- \hj||_{\mn}$ from \cref{cmt2mn}.

>>>>

&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\mn}

@@

+||\Gamma J^*-\hg J^*||_{\mn}+||\hj-\hg\hj||_{\mn}\big).

@@

Now in a manner similar to \cref{cmt2mn} we have
||J^*- \hj||_{\mn}&\leq ||J^*- \hv||_{\mn}+||\hv -\hj||_{\mn}\nn
The result now follows by substituting the bound on $||J^*- \hv||_{\mn}$ from \cref{cmt1mn} and the fact that $||\hv-\hj||_{\mn}\leq \frac{1}{1-\beta_{\psi}}||\hj-\hg\hj||$.
